Learning by Teaching a Robot: the Case of Handwriting

### 2015-07-08 main.tex
WIP intro

This research departs from the traditional approaches to educative robotics
(\fixme{cite reviews})

@@

However, we believe that the strongest impact of this work is for the
human-robot interaction community and relates to the very \emph{nature} of the
interaction fostered by this research. The work presented here investigates a
particular role for a robot in the education of handwriting: not only is the
robot actively performing the activity by drawing letters, but it does so in a
way that engages the child in a very specific social role. The child is the
teacher in this relationship and the robot is the learner: the child must engage
in a (meta-) cognitive relationship with the robot to try to understand why the
robot fails and how to help it best.  Here, the robot is more than just an
activity facilitator or orchestrator -- its physical presence and embodiment
induce agency and anthropomorphising, and cognitively engage the child into the
learning activity, which we predict will lead to higher learning efficacy.

>>>>

This research departs from the traditional approaches to educative robotics
\cite{barker2007robotics,karim2015review}.

@@

The work presented here investigates a particular role for a robot in the
education of handwriting: not only is the robot actively performing the activity
by drawing letters, but it does so in a way that engages the child in a very
specific social role. The child is the teacher in this relationship and the
robot is the learner: the child must engage in a (meta-) cognitive relationship
with the robot to try to understand why the robot fails and how to help it best.
Here, the robot is more than just an activity facilitator or orchestrator -- its
physical presence and embodiment induce agency and anthropomorphising, and
cognitively engage the child into the learning activity.

Besides that, the commitment of the child into the interaction build on the
``protégé effect'': teachable computer-based agents have previously been used to
encourage the ``protégé effect'', wherein students invest more effort into
learning when it is for a teachable agent than for themselves~\cite{Chase2009}.
As we are concerned with learning of a physical skill, the learning agent
developed is embodied in a humanoid robot which is capable of physically
demonstrating handwriting trajectories to its child learning partner.  This is
supported by the potential for motor mimicry to yield significant improvements
in handwriting interventions in which letter formations are demonstrated to
participants~\cite{Berninger1997}. Furthermore, when compared to screen-based
agents, robotic partners have been shown in some contexts to increase users'
compliance with tasks~\cite{Bainbridge2011}, maintain more effective long-term
relationships~\cite{Kidd2008}, and produce greater learning gains when acting as
tutors~\cite{Leyzberg2012}.

For these two reasons, our approach is to be distinguished from previous works in
educational robotic. Most of these do not consider the agency induced by the
robot beyond its motivational aspect: playing with an interactive, partially autonomous
device naturally induces some form of anthropomorphizing, which leads to some
level of projected agency, and participate the overall excitement (at least, on
the short-term, before the novelty effect vanishes).

In our case, the role of agency is stronger: it induces meta-cognition (``I am
interacting with an agent, so I need to reflect on how to best teach him''),
which is beneficial for the learning process; it also induces a protégé effect
(``I want my robot-agent to succeed!'') which support the commitment of child
into the interaction, also for longer period of time (we report in this article
upon to case studies where children were interacting with the same robot for several
hours, spanned over several weeks).
